---
title: "Correlation"
author: "Huiting Su"
date: "April 4, 2018"
output: html_document
---

### See how correlation influence. 

```{r}
#library(MASS)
library(glmnet)
```

n: the number of samples ("rows" of data) required.
mu: a vector giving the means of the variables.
Sigma: positive-definite symmetric matrix specifying the covariance matrix of the variables.

The problem: n x p -> 3 x 4. N(0, 1)


### Define the global variable X, y1, y2, y3.
```{r}
set.seed(65587)
# n = 2500, p = 4 
X <- matrix(rnorm(10000), 2500, 4)

# Have 3 different responses
y1 <- 0.9 * X[, 1] + 0.00 * X[, 2] + 1.2 * X[, 3] + 0.3 * X[, 4]
y2 <- 1.1 * X[, 1] + 0.02 * X[, 2] + 0.8 * X[, 3] + 0.4 * X[, 4]
y3 <- 0.9 * X[, 1] + 0.01 * X[, 2] + 1.3 * X[, 3] + 0.5 * X[, 4]

w = c(0.9, 0.00, 1.2, 0.3, 1.1, 0.02, 0.8, 0.4, 0.9, 0.01, 1.3, 0.5)
w = matrix(w, 4, 3)
```

### Function for multi-task LASSO experiment
```{r}
mt_LASSO <- function(Cov){
    set.seed(12345)
    # epsilon is the gaussian error. dimension: n * 3. 
    epsilon <- MASS::mvrnorm(n=2500, mu = rep(0, 3), Sigma = Cov)
    y <- cbind(y1, y2, y3)  
    y <- y + epsilon
    
    mt_fit = glmnet(X, y, family = "mgaussian")
    plot(mt_fit, type.coef = "2norm", label = TRUE)
    
    ## Use Cross Validation to select $\lambda$, and compare.
    cv.mt_fit = cv.glmnet(X, y, family = "mgaussian", intercept = FALSE)
    cv.fit1 = cv.glmnet(X, y[, 1], intercept = FALSE)
    cv.fit2 = cv.glmnet(X, y[, 2], intercept = FALSE)
    cv.fit3 = cv.glmnet(X, y[, 3], intercept = FALSE)
    #plot(cv.mt_fit)
    #plot(cv.fit1)
    #plot(cv.fit2)
    #plot(cv.fit3)
    
    # multi-task
    mt_beta = cbind(coef(cv.mt_fit)$y1, coef(cv.mt_fit)$y2, coef(cv.mt_fit)$y3)
    mt_beta = mt_beta[-1,]
    print(mt_beta)
    print( sum((mt_beta - w)^2) )
    
    # lasso for each response
    lasso_beta = cbind(coef(cv.fit1), coef(cv.fit2), coef(cv.fit3))
    lasso_beta = lasso_beta[-1,]
    print(lasso_beta)
    print( sum((lasso_beta - w)^2) )
}
```




1. No correlation.
```{r}
Cov1 = diag(3)
Cov1
mt_LASSO(Cov1)
```

2. Positive correlation
2.1 Identical
```{r}
Cov2 = matrix(rep(1, 9), 3, 3) 
Cov2
mt_LASSO(Cov2)
```
2.2 
```{r}
Cov3 = matrix(rep(0.5, 9), 3, 3) + diag(0.5,3) 
Cov3
mt_LASSO(Cov3)
```

2.3
```{r}
set.seed(12345)
Cov4 = diag(3) 
Cov4[lower.tri(Cov4, diag = FALSE)] = runif(3, min=0, max=1)
Cov4[upper.tri(Cov4, diag = FALSE)] = Cov4[lower.tri(Cov4, diag = FALSE)]
Cov4
mt_LASSO(Cov4)
```

2.4
```{r}
set.seed(7749)
Cov5 = diag(3) 
Cov5[lower.tri(Cov5, diag = FALSE)] = runif(3, min=0, max=1)
Cov5[upper.tri(Cov5, diag = FALSE)] = Cov5[lower.tri(Cov5, diag = FALSE)]
print(Cov5)
mt_LASSO(Cov5)
```

3. Nested
3.1 
```{r}
Cov2n = Cov2
Cov2n[upper.tri(Cov2n, diag = FALSE)] = Cov2n[upper.tri(Cov2n, diag = FALSE)] * c(1/3, -1/3, 1/3)
Cov2n[lower.tri(Cov2n, diag = FALSE)] = Cov2n[upper.tri(Cov2n, diag = FALSE)]
print(Cov2n)
mt_LASSO(Cov2n)
```

3.2 
```{r}
Cov3n = Cov3
Cov3n[upper.tri(Cov3n, diag = FALSE)] = Cov3n[upper.tri(Cov3n, diag = FALSE)] * c(1, -1, 1)
Cov3n[lower.tri(Cov3n, diag = FALSE)] = Cov3n[upper.tri(Cov3n, diag = FALSE)]
print(Cov3n)
mt_LASSO(Cov3n)
```

3.3 
```{r}
Cov5n = Cov5
Cov5n[upper.tri(Cov5n, diag = FALSE)] = Cov5n[upper.tri(Cov5n, diag = FALSE)] * c(1, -1, 1)
Cov5n[lower.tri(Cov5n, diag = FALSE)] = Cov5n[upper.tri(Cov5n, diag = FALSE)]
print(Cov5n)
mt_LASSO(Cov5n)
```





