---
title: "Correlation"
author: "Huiting Su"
date: "April 4, 2018"
output: html_document
---

## See how correlation influence. 

```{r, warning=False, message=False}
library(MASS)
library(rockchalk)
```

n: the number of samples ("rows" of data) required.
mu: a vector giving the means of the variables.
Sigma: positive-definite symmetric matrix specifying the covariance matrix of the variables.

```{r}
#myR <- lazyCor(X = 0.3, d = 3)
#mySD <- c(0.5, 0.5, 0.5) # 1.5, 1.5)
#myCov <- lazyCov(Rho = myR, Sd = mySD)
myCov = 
set.seed(12345)
X0 <- MASS::mvrnorm(n=2500, mu = rep(0, 3), Sigma = myCov)
## create a smaller data set, starting at same position
```

```{r}
set.seed(65587)
x <- matrix(rnorm(10000), 2500, 4)
#x <- as.data.frame(x)
#colnames(x) <- c('x1', 'x2', 'x3', 'x4')

y1 <- 0.9*x[,1] + 0.00*x[,2] + 1.2*x[,3] + 0.3*x[,4]
y2 <- 1.1*x[,1] + 0.02*x[,2] + 0.8*x[,3] + 0.4*x[,4]
y3 <- 0.9*x[,1] + 0.01*x[,2] + 1.3*x[,3] + 0.5*x[,4]
y <- cbind(y1, y2, y3)
y <- y + 0.1*X0
```

```{r}
mfit = glmnet(x, y, family = "mgaussian")
plot(mfit,type.coef="2norm", label = TRUE)
```

## Use Cross Validation to select $\lambda$, and compare.
```{r}
cv.mfit = cv.glmnet(x, y, family = "mgaussian")
cv.fit1 = cv.glmnet(x, y[,1])
cv.fit2 = cv.glmnet(x, y[,2])
cv.fit3 = cv.glmnet(x, y[,3])
plot(cv.mfit)
plot(cv.fit1)
plot(cv.fit2)
plot(cv.fit3)
```

```{r}
# multi-task
cbind(coef(cv.mfit)$y1, coef(cv.mfit)$y2, coef(cv.mfit)$y3)

# lasso for each response
cbind(coef(cv.fit1), coef(cv.fit2), coef(cv.fit3))
```





## larger error
```{r}
set.seed(65587)
x <- matrix(rnorm(10000), 2500, 4)
#x <- as.data.frame(x)
#colnames(x) <- c('x1', 'x2', 'x3', 'x4')

y1 <- 0.9*x[,1] + 0.00*x[,2] + 1.2*x[,3] + 0.3*x[,4]
y2 <- 1.1*x[,1] + 0.02*x[,2] + 0.8*x[,3] + 0.4*x[,4]
y3 <- 0.9*x[,1] + 0.01*x[,2] + 1.3*x[,3] + 0.5*x[,4]
y <- cbind(y1, y2, y3)
y <- y + X0
```

```{r}
mfit = glmnet(x, y, family = "mgaussian")
plot(mfit,type.coef="2norm", label = TRUE)
```

## Use Cross Validation to select $\lambda$, and compare.
```{r}
cv.mfit = cv.glmnet(x, y, family = "mgaussian")
cv.fit1 = cv.glmnet(x, y[,1])
cv.fit2 = cv.glmnet(x, y[,2])
cv.fit3 = cv.glmnet(x, y[,3])
plot(cv.mfit)
plot(cv.fit1)
plot(cv.fit2)
plot(cv.fit3)
```

```{r}
# multi-task
cbind(coef(cv.mfit)$y1, coef(cv.mfit)$y2, coef(cv.mfit)$y3)

# lasso for each response
cbind(coef(cv.fit1), coef(cv.fit2), coef(cv.fit3))
```






## Correlation structure 
```{r}
set.seed(12345)
X0 <- MASS::mvrnorm(n=2500, mu = rep(0, 3), Sigma = diag(3))
```

```{r}
set.seed(65587)
x <- matrix(rnorm(10000), 2500, 4)
#x <- as.data.frame(x)
#colnames(x) <- c('x1', 'x2', 'x3', 'x4')

y1 <- 0.9*x[,1] + 0.00*x[,2] + 1.2*x[,3] + 0.3*x[,4]
y2 <- 1.1*x[,1] + 0.02*x[,2] + 0.8*x[,3] + 0.4*x[,4]
y3 <- 0.9*x[,1] + 0.01*x[,2] + 1.3*x[,3] + 0.5*x[,4]
y <- cbind(y1, y2, y3)
y <- y + 0.1*X0
```

```{r}
mfit = glmnet(x, y, family = "mgaussian")
plot(mfit,type.coef="2norm", label = TRUE)
```

## Use Cross Validation to select $\lambda$, and compare.
```{r}
cv.mfit = cv.glmnet(x, y, family = "mgaussian")
cv.fit1 = cv.glmnet(x, y[,1])
cv.fit2 = cv.glmnet(x, y[,2])
cv.fit3 = cv.glmnet(x, y[,3])
plot(cv.mfit)
plot(cv.fit1)
plot(cv.fit2)
plot(cv.fit3)
```

```{r}
# multi-task
cbind(coef(cv.mfit)$y1, coef(cv.mfit)$y2, coef(cv.mfit)$y3)

# lasso for each response
cbind(coef(cv.fit1), coef(cv.fit2), coef(cv.fit3))
```

