---
title: "SSD multi-task lasso vs lasso 1216"
author: "Huiting Su"
date: "April 4, 2018"
output: html_document
---
I want to test if I select random 3 factors, but the 3 factors are important for all tasks, whether the performance will be better.


Design: 1216  
beta ~ N(0,1)  
True factors: same for each task -- first 3 factors.

n: the number of samples ("rows" of data) required.
mu: a vector giving the means of the variables.
Sigma: positive-definite symmetric matrix specifying the covariance matrix of the variables.

X: n x p  N(0, 1)
p: number of factors
l: number of tasks
y: n x l  response
epsilon : n x l  noise
w : p x l. wij is the coef of factor i for task j

```{r, warning= FALSE, message = FALSE, echo=FALSE}
#library(MASS)
library(glmnet)
```

## Initialization
### (n=12, p=16) q in [1,3] 3, l = 5
```{r}
#set.seed(65587)
n_rep <- 100
a <- 5  # absolute value of true factor

n <- 12
p <- 16
l <- 5
q <- 3
X <- read.csv("design1226.csv", skip = 7, header = FALSE)
X <- apply(X, 1, gsub, pattern="\\+", replacement= "1", perl=TRUE)
X <- apply(X, 1, gsub, pattern="\\-", replacement= "-1", perl=TRUE)
X <- matrix(as.numeric(X), n, p)

lasso_OC <<- numeric()
mt_OC <<- numeric()
lasso_SC <<- numeric()
mt_SC <<- numeric()

lasso_OC2 <<- numeric()
mt_OC2 <<- numeric()
lasso_SC2 <<- numeric()
mt_SC2 <<- numeric()
```

### Define the global variable X, w, y. Replicate 10000 times.
```{r}
getXy <- function(){
    # Have 5 different responses
    # There are 3 same true var for different tasks, the true vars are randomly chosen
    
    # for every task, we need a vector to set the true vars
    w <<- matrix(0, p, l)
    true_var <- c(1, 2)    #sample(p, q)  #c(1, 2, 3)   #
    for (j in 1:l) {
        w[true_var, j] <<- a # runif(3, 3, 5)
    }
    #######print(w)
    y <<- X %*% w
    # epsilon is the gaussian error. dimension: n * l.
    epsilon <- matrix(rnorm(n * l), n, l)
    
    y <<- y + epsilon
}
```


### Function for multi-task LASSO experiment
```{r}
compare <- function() {
    mt_fit = glmnet(X, y, family = "mgaussian")
    #plot(mt_fit, type.coef = "2norm", label = TRUE)
    
    ## Use Cross Validation to select $\lambda$, and compare.
    cv.mt_fit = cv.glmnet(X, y, family = "mgaussian", intercept = FALSE)
    cv.fit1 = cv.glmnet(X, y[, 1], intercept = FALSE)
    cv.fit2 = cv.glmnet(X, y[, 2], intercept = FALSE)
    cv.fit3 = cv.glmnet(X, y[, 3], intercept = FALSE)
    cv.fit4 = cv.glmnet(X, y[, 4], intercept = FALSE)
    cv.fit5 = cv.glmnet(X, y[, 5], intercept = FALSE)
    # Option grouped=FALSE enforced in cv.glmnet, since < 3 observations per fold
    # If grouped=FALSE, an error matrix is built up at the observation level from the predictions from the nfold fits, and then summarized
    
    #plot(cv.mt_fit)
    #plot(cv.fit1)
    #plot(cv.fit2)
    #plot(cv.fit3)
    
    # multi-task
    mt_beta = numeric()
    for(i in 1:l){
        mt_beta = cbind(mt_beta,  eval(parse(text = paste('coef(cv.mt_fit)$y', i, sep=''))) )
    }
    mt_beta = mt_beta[-1,]
    #####print(mt_beta)
    
    
    # lasso for each response
    lasso_beta = numeric()
    for(i in 1:l){
        lasso_beta = cbind(lasso_beta,  eval(parse(text = paste('coef(cv.fit', i,')', sep=''))) )
    }
    lasso_beta = lasso_beta[-1,]
    ####print(lasso_beta)
    
    # get whether correct selection
    mt_OC <<- c(mt_OC, sum(as.logical(w) == as.logical(mt_beta)) == p*l )
    lasso_OC <<- c(lasso_OC, sum(as.logical(w) == as.logical(lasso_beta)) == p * l)
    
    mt_SC <<- c(mt_SC, sum(sign(w) == sign(mt_beta)) == p*l )
    lasso_SC <<- c(lasso_SC, sum(sign(w) == sign(lasso_beta)) == p*l )
    
    #
    mt_OC2 <<- c(mt_OC2, sum(as.logical(w) == as.logical(mt_beta)) / (p * l))
    lasso_OC2 <<- c(lasso_OC2, sum(as.logical(w) == as.logical(lasso_beta)) / (p * l))
    
    mt_SC2 <<- c(mt_SC2, sum(sign(w) == sign(mt_beta)) / (p * l))
    lasso_SC2 <<- c(lasso_SC2, sum(sign(w) == sign(lasso_beta)) / (p * l))
}

```

Main function
```{r, warning=FALSE, message=FALSE, cache=TRUE}
set.seed(87293)
for(ii in 1:n_rep){
    getXy()
    compare()
}
#print(mt_OC)
#print(lasso_OC)

cat(mean(mt_OC), mean(lasso_OC), mean(mt_SC), mean(lasso_SC), mean(mt_OC2), mean(lasso_OC2), mean(mt_SC2), mean(lasso_SC2))
cat(
    rbind(
        t.test(mt_OC)$conf.int[1:2],
        t.test(lasso_OC)$conf.int[1:2],
        t.test(mt_SC)$conf.int[1:2],
        t.test(lasso_SC)$conf.int[1:2],
        t.test(mt_OC2)$conf.int[1:2],
        t.test(lasso_OC2)$conf.int[1:2],
        t.test(mt_SC2)$conf.int[1:2],
        t.test(lasso_SC2)$conf.int[1:2])
    )
```

Analysis of the matrix:
Calculation of E(s^2): 
```{r}
sums <- 0
pp <- 16
for(i in 1:(pp-1))
    for(j in (i+1):pp){
        s <- t(X[,i]) %*% X[,j]
        sums <- sums + s^2
    }
sums <- sums * 2/ pp /(pp-1)
```

total E(s^2): 5.2
sums 14~16: 16
sums 1~3: 32
     2~4: 48
     4~6: 0
sums 8~10: 16
sums 5~7: 16


The first 3 factors are significant, so compare the first columns.


Calculate RSS:
1. Every two column
```{r}
sums <- 0
pp <- 16

for(a1 in 1:(pp-1))
    for(a2 in (a1+1):pp){
        XC <- X[,-c(a1, a2)]
        XA <- X[, c(a1, a2)]
        invXA <- solve(t(XA) %*% XA)
        s <- t(XC) %*% XA %*% invXA %*% invXA %*% t(XA) %*% XC 
        #cat(a1, a2, sum(diag(s)), "\n")
        sums <- sums + sum(diag(s))
    }
```        

2. Every three column
```{r}                
sums <- 0
pp <- 16

for(a1 in 1:(pp-2))
    for(a2 in (a1+1):(pp-1))
        for(a3 in (a2+1):(pp-1)){
            XC <- X[,-c(a1, a2, a3)]
            XA <- X[, c(a1, a2, a3)]
            invXA <- solve(t(XA) %*% XA)
            s <- t(XC) %*% XA %*% invXA %*% invXA %*% t(XA) %*% XC 
            cat(a1, a2, a3, sum(diag(s)), "\n")
            sums <- sums + sum(diag(s))
    }
```


Linear relation
1. for every 2 columns
```{r}
pp <- 16
diff2 <- numeric()
for(a1 in 1:(pp-1))
    for(a2 in (a1+1):pp)
            for(b in 1:pp){
                if(a1 != b && a2 != b){
                    diff2 <- cbind(diff2, X[,a1]+X[,a2]-X[,b]) 
                } 
            }
```

2. for every 3 columns
```{r}
pp <- 16
diff3 <- numeric()
for(a1 in 1:(pp-2))
    for(a2 in (a1+1):(pp-1))
        for(a3 in (a2+1):pp)
            for(b in 1:pp){
                if(a1 != b && a2 != b && a3 != b){
                    diff3 <- cbind(diff3, X[,a1]+X[,a2]+X[,a3]-X[,b]) 
                } 
            }
            
```





